---
title: "NFL Combine Athletic Testing and Position Production Analysis"
author: "Ronish Padhy"
date: "May 6, 2026"
format:
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
# Load packages used in this analysis.
# Install these in the Console first if needed:
# install.packages(c("tidyverse", "ggplot2", "knitr", "stringr", "remotes"))
# install.packages("nflreadr", repos = c("https://nflverse.r-universe.dev", getOption("repos")))

library(tidyverse)
library(nflreadr)
library(ggplot2)
library(knitr)
library(stringr)

# Seasons included in the analysis.
years <- 2016:2025

# Load NFL Combine data and weekly player stats.
Combine_All <- purrr::map_dfr(years, load_combine)
Player_Stats_All <- purrr::map_dfr(years, load_player_stats)

# Convert height values into inches when the original height is stored
# as a football-style value such as "5-11".
clean_height_inches <- function(height_value) {
  height_chr <- as.character(height_value)

  dplyr::case_when(
    stringr::str_detect(height_chr, "^\\d-\\d{1,2}$") ~
      as.numeric(stringr::str_extract(height_chr, "^\\d")) * 12 +
      as.numeric(stringr::str_extract(height_chr, "\\d{1,2}$")),

    suppressWarnings(!is.na(as.numeric(height_chr))) ~
      as.numeric(height_chr),

    TRUE ~ NA_real_
  )
}

# Create a position-level Combine summary table.
make_combine_table <- function(position_code) {
  Combine_All |>
    filter(pos == position_code) |>
    mutate(height_inches = clean_height_inches(ht)) |>
    group_by(season) |>
    summarise(
      player_count = n(),
      avg_height_inches = round(mean(height_inches, na.rm = TRUE), 1),
      avg_weight = round(mean(wt, na.rm = TRUE), 1),
      avg_forty = round(mean(forty, na.rm = TRUE), 2),
      avg_vertical = round(mean(vertical, na.rm = TRUE), 1),
      avg_bench = round(mean(bench, na.rm = TRUE), 1),
      avg_cone = round(mean(cone, na.rm = TRUE), 2),
      .groups = "drop"
    ) |>
    arrange(season)
}

WR_Combine_Table <- make_combine_table("WR")
RB_Combine_Table <- make_combine_table("RB")

# Build average receiving yards per game for WRs.
WR_YPG_Avg <- Player_Stats_All |>
  filter(position == "WR", season_type == "REG") |>
  group_by(season, player_id, player_name) |>
  summarise(
    games_played = n_distinct(week),
    total_rec_yards = sum(receiving_yards, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(games_played >= 3) |>
  mutate(player_ypg = total_rec_yards / games_played) |>
  group_by(season) |>
  summarise(avg_wr_ypg = mean(player_ypg, na.rm = TRUE), .groups = "drop")

# Build average rushing yards per game for RBs.
RB_YPG_Avg <- Player_Stats_All |>
  filter(position == "RB", season_type == "REG") |>
  group_by(season, player_id, player_name) |>
  summarise(
    games_played = n_distinct(week),
    total_rushing = sum(rushing_yards, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(games_played >= 3) |>
  mutate(player_ypg = total_rushing / games_played) |>
  group_by(season) |>
  summarise(avg_rb_ypg = mean(player_ypg, na.rm = TRUE), .groups = "drop")

# Helper function for dual-axis plots.
make_dual_axis_plot <- function(data, x_var, athletic_var, production_var,
                                athletic_label, production_label,
                                title_text, subtitle_text) {

  athletic_range <- range(data[[athletic_var]], na.rm = TRUE)
  production_range <- range(data[[production_var]], na.rm = TRUE)

  scale_factor <- diff(athletic_range) / diff(production_range)
  shift <- athletic_range[1] - production_range[1] * scale_factor

  plot_data <- data |>
    mutate(production_scaled = .data[[production_var]] * scale_factor + shift)

  ggplot(plot_data, aes(x = .data[[x_var]])) +
    geom_line(aes(y = .data[[athletic_var]], color = athletic_label),
              linewidth = 1.2) +
    geom_point(aes(y = .data[[athletic_var]], color = athletic_label),
               size = 3) +
    geom_line(aes(y = production_scaled, color = production_label),
              linewidth = 1.2, linetype = "dashed") +
    geom_point(aes(y = production_scaled, color = production_label),
               size = 3) +
    scale_y_continuous(
      name = athletic_label,
      sec.axis = sec_axis(
        transform = ~ (. - shift) / scale_factor,
        name = production_label
      )
    ) +
    scale_x_continuous(breaks = years) +
    scale_color_manual(
      values = c(
        athletic_label = "#003f5c",
        production_label = "#ff6361"
      )
    ) +
    labs(
      title = title_text,
      subtitle = subtitle_text,
      x = "Season / Combine Year",
      color = NULL
    ) +
    theme_minimal(base_size = 13) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5, color = "grey40"),
      legend.position = "bottom"
    )
}

# WR three-cone data and plot.
Combine_WR_Cone_Avg <- Combine_All |>
  filter(pos == "WR", !is.na(cone)) |>
  group_by(season) |>
  summarise(avg_cone = mean(cone, na.rm = TRUE), .groups = "drop")

TCD_WRYPG_Data <- inner_join(Combine_WR_Cone_Avg, WR_YPG_Avg, by = "season")

TCD_WRYPG_Plot <- make_dual_axis_plot(
  data = TCD_WRYPG_Data,
  x_var = "season",
  athletic_var = "avg_cone",
  production_var = "avg_wr_ypg",
  athletic_label = "Avg 3-Cone Drill Time (seconds) — lower is faster",
  production_label = "Avg WR Receiving Yards Per Game",
  title_text = "NFL Combine WR 3-Cone Drill vs. WR Receiving Yards Per Game",
  subtitle_text = "Combine classes 2016–2025 | Regular season stats 2016–2025"
)

# WR forty-yard dash data and plot.
Combine_WR_Forty_Avg <- Combine_All |>
  filter(pos == "WR", !is.na(forty)) |>
  group_by(season) |>
  summarise(avg_forty = mean(forty, na.rm = TRUE), .groups = "drop")

Forty_WRYPG_Data <- inner_join(Combine_WR_Forty_Avg, WR_YPG_Avg, by = "season")

Forty_WRYPG_Plot <- make_dual_axis_plot(
  data = Forty_WRYPG_Data,
  x_var = "season",
  athletic_var = "avg_forty",
  production_var = "avg_wr_ypg",
  athletic_label = "Avg 40-Yard Dash Time (seconds) — lower is faster",
  production_label = "Avg WR Receiving Yards Per Game",
  title_text = "NFL Combine WR 40-Yard Dash vs. WR Receiving Yards Per Game",
  subtitle_text = "Combine classes 2016–2025 | Regular season stats 2016–2025"
)

# RB three-cone data and plot.
Combine_RB_Cone_Avg <- Combine_All |>
  filter(pos == "RB", !is.na(cone)) |>
  group_by(season) |>
  summarise(avg_cone = mean(cone, na.rm = TRUE), .groups = "drop")

TCD_RBYPG_Data <- inner_join(Combine_RB_Cone_Avg, RB_YPG_Avg, by = "season")

TCD_RBYPG_Plot <- make_dual_axis_plot(
  data = TCD_RBYPG_Data,
  x_var = "season",
  athletic_var = "avg_cone",
  production_var = "avg_rb_ypg",
  athletic_label = "Avg 3-Cone Drill Time (seconds) — lower is faster",
  production_label = "Avg RB Rushing Yards Per Game",
  title_text = "NFL Combine RB 3-Cone Drill vs. RB Rushing Yards Per Game",
  subtitle_text = "Combine classes 2016–2025 | Regular season stats 2016–2025"
)

# RB forty-yard dash data and plot.
Combine_RB_Forty_Avg <- Combine_All |>
  filter(pos == "RB", !is.na(forty)) |>
  group_by(season) |>
  summarise(avg_forty = mean(forty, na.rm = TRUE), .groups = "drop")

Forty_RBYPG_Data <- inner_join(Combine_RB_Forty_Avg, RB_YPG_Avg, by = "season")

Forty_RBYPG_Plot <- make_dual_axis_plot(
  data = Forty_RBYPG_Data,
  x_var = "season",
  athletic_var = "avg_forty",
  production_var = "avg_rb_ypg",
  athletic_label = "Avg 40-Yard Dash Time (seconds) — lower is faster",
  production_label = "Avg RB Rushing Yards Per Game",
  title_text = "NFL Combine RB 40-Yard Dash vs. RB Rushing Yards Per Game",
  subtitle_text = "Combine classes 2016–2025 | Regular season stats 2016–2025"
)
```

# Busiest Airports Analysis

For this version of the assignment, I adapted the required analysis structure to my NFL data context. Instead of studying the six busiest airports, this section studies NFL Combine results for wide receivers and running backs from 2016 through 2025. The goal is to summarize how the average physical testing profile changed by season and then connect those testing results to position-specific production.

The tables below summarize the average measurements and drill results for each position by season. I included player count, height, weight, 40-yard dash time, vertical jump, bench press, and three-cone drill time because these are common Combine measurements used to describe speed, explosiveness, strength, and change-of-direction ability. For both wide receivers and running backs, lower 40-yard dash and three-cone times represent faster performances, while higher vertical and bench values represent better explosiveness or strength.

```{r wr-table}
kable(
  WR_Combine_Table,
  caption = "Table 1. Average NFL Combine Measurements for Wide Receivers by Season",
  col.names = c(
    "Season",
    "WR Count",
    "Avg Height (inches)",
    "Avg Weight",
    "Avg 40-Yard Dash",
    "Avg Vertical",
    "Avg Bench Reps",
    "Avg 3-Cone"
  )
)
```

The wide receiver table gives a season-by-season view of how the average WR Combine profile changed across the sample. This is useful because wide receiver production depends on more than one athletic trait. Straight-line speed matters, but so do agility, body size, and explosiveness. The table also helps avoid judging the position based on one drill alone.

```{r rb-table}
kable(
  RB_Combine_Table,
  caption = "Table 2. Average NFL Combine Measurements for Running Backs by Season",
  col.names = c(
    "Season",
    "RB Count",
    "Avg Height (inches)",
    "Avg Weight",
    "Avg 40-Yard Dash",
    "Avg Vertical",
    "Avg Bench Reps",
    "Avg 3-Cone"
  )
)
```

The running back table focuses on the same testing categories, but the interpretation is slightly different. For running backs, the 40-yard dash can show long-speed potential, while the three-cone drill can connect more closely to change of direction, short-area movement, and cutting ability. These traits do not guarantee NFL production, but they give a structured way to compare Combine classes over time.

# Monte Carlo Numerical Integration

For this adapted version, I use the visualization section to compare Combine testing averages with regular season production. The original assignment asked for a Monte Carlo visualization, but the same reproducible-document goal still applies here: the reader should be able to see how the code creates a plot, understand what is being compared, and interpret the result from the written explanation.

The plots use dual axes because drill times and yards per game are measured on different scales. The solid line shows the average Combine drill result for each season, and the dashed line shows average position production per game. For wide receivers, production is measured by receiving yards per game. For running backs, production is measured by rushing yards per game.

```{r wr-cone-plot, fig.width=8, fig.height=5}
TCD_WRYPG_Plot
```

This graph compares average wide receiver three-cone drill time to average wide receiver receiving yards per game. Since lower three-cone times are better, a downward movement in the drill line represents better average agility testing. The main purpose of this graph is not to claim that the three-cone drill directly causes receiving production. Instead, it shows whether average agility testing and average receiving output moved together across the same seasons.

```{r wr-forty-plot, fig.width=8, fig.height=5}
Forty_WRYPG_Plot
```

This graph compares average wide receiver 40-yard dash time to average wide receiver receiving yards per game. The 40-yard dash is a straight-line speed test, while receiving yards per game depends on many football factors such as route running, role, quarterback play, targets, and offensive scheme. Because of that, the graph should be read as a descriptive comparison rather than proof that faster Combine times automatically create higher production.

```{r rb-cone-plot, fig.width=8, fig.height=5}
TCD_RBYPG_Plot
```

This graph compares average running back three-cone drill time to average running back rushing yards per game. For running backs, change of direction can matter because the position requires cutting, reacting to blocking, and creating yards through traffic. Still, rushing yards per game is also shaped by team offensive line quality, game script, carry volume, and role. The graph is useful because it gives a first look at whether Combine agility averages and rushing production move in the same direction over time.

```{r rb-forty-plot, fig.width=8, fig.height=5}
Forty_RBYPG_Plot
```

This graph compares average running back 40-yard dash time to average running back rushing yards per game. A faster 40-yard dash may help a back create explosive plays, but rushing production is not only a speed stat. This plot helps show whether the average speed profile of Combine running backs lines up with average rushing yards per game during the same seasons.

# Planning and Prompting GenAI Tools

Before using a GenAI tool, I developed a plan for tidying, wrangling, and visualizing the data. My data context includes two main sources from the `nflreadr` package: NFL Combine data and weekly player statistics. The Combine data contains athletic testing information, while the player stats data contains season and weekly production.

My plan was:

1. Load Combine data and player statistics from 2016 through 2025.
2. Combine the separate yearly data frames into one data frame for Combine results and one data frame for player stats.
3. Filter Combine results to wide receivers and running backs.
4. Remove missing values from the drill being analyzed, such as the three-cone drill or 40-yard dash.
5. Group by season and calculate average Combine drill results.
6. Filter weekly player stats to regular season data only.
7. Group by season and player to calculate each player's total yards and games played.
8. Remove players with fewer than three games played so that small-sample players do not distort the average.
9. Calculate each player's yards per game.
10. Group by season and calculate the average yards per game for the position.
11. Join the Combine summary table with the player production summary table.
12. Create line graphs comparing average Combine testing results with average position-specific yards per game.
13. Write a narrative explaining that the graphs show descriptive patterns, not direct causation.

The plan-based prompt gave the GenAI tool a clear direction. It specified the positions, years, data sources, filters, summary statistics, and plot type. Because of that, the generated result was more focused and easier to adapt into working R code.

The generic prompt was less specific. A generic prompt such as “make an NFL Combine graph using R” might produce a graph, but it would not necessarily know which positions to use, what production stat to compare, how to handle missing values, or how to avoid tiny sample sizes. The plan-based result was stronger because it was tied to the actual data structure and the specific research question.

The biggest difference between the two prompting styles was control. The plan-based prompt acted like a map, while the generic prompt acted more like a guess. The plan-based version produced code that matched my goal more closely and required less cleanup.

# Reflection

This assignment helped me understand why reproducible documents matter. Before using Quarto, my code and written explanation felt more separate. The code lived in one place, and the final explanation lived somewhere else. In a Quarto document, both pieces connect in one workflow, which makes the final analysis easier to check, edit, and update.

One specific thing I learned was how important it is to hide code in the main report while still preserving it in the appendix. The reader should not have to work through every line of code to understand the analysis. At the same time, the code still needs to be available so someone else can verify how the results were made.

I also learned that data analysis depends heavily on the choices made before plotting. For example, I filtered out players with fewer than three games played because extremely small samples can make yards per game misleading. That decision changes the quality of the analysis. It also shows that cleaning and filtering data is not just a technical step. It affects the argument being made.

Finally, this assignment showed me that GenAI tools are more useful when the prompt includes a real plan. When I gave the tool a clear sequence of steps, the output was more relevant. When the prompt was too general, the result was less connected to the actual assignment goal. That made me realize that GenAI does not replace planning. It works better when the human already knows what needs to happen.

# GenAI Usage Appendix

## Tool Used

ChatGPT, GPT-5.5 Thinking.

## Date of Usage

May 6, 2026.

## Prompt 1

“is thiswr and rb”

## Response 1

The response explained that the first uploaded code was wide receiver only because the code used `filter(pos == "WR")` for Combine data and `filter(position == "WR")` for player statistics. It also explained that running backs should use rushing yards per game rather than receiving yards per game unless the analysis is specifically about pass-catching running backs.

## Prompt 2

“make a quarto file with this and this and make sure it has In this assignment, you'll be creating your first reproducible data analysis document through the use of Quarto... [assignment requirements provided] ... but relative to this code ofc”

## Response 2

The response generated this Quarto document. It combined the wide receiver and running back NFL Combine code, added a YAML header, organized the document with section headings, hid code from the main report, included narrative text, added a GenAI usage appendix, and added a code appendix.

# Code Appendix

The code below contains the main code used to produce the tables and graphs in this report.

```{r code-appendix, eval=FALSE, echo=TRUE}
# Step 1: Load Packages ----
# Install these in the Console first if needed:
# install.packages(c("tidyverse", "ggplot2", "knitr", "stringr", "remotes"))
# install.packages("nflreadr", repos = c("https://nflverse.r-universe.dev", getOption("repos")))

library(tidyverse)
library(nflreadr)
library(ggplot2)
library(knitr)
library(stringr)

# Step 2: Load Data ----
years <- 2016:2025

# Load all Combine data and player stats from 2016 through 2025.
Combine_All <- purrr::map_dfr(years, load_combine)
Player_Stats_All <- purrr::map_dfr(years, load_player_stats)

# Step 3: Clean Height Values ----
clean_height_inches <- function(height_value) {
  height_chr <- as.character(height_value)

  dplyr::case_when(
    stringr::str_detect(height_chr, "^\\d-\\d{1,2}$") ~
      as.numeric(stringr::str_extract(height_chr, "^\\d")) * 12 +
      as.numeric(stringr::str_extract(height_chr, "\\d{1,2}$")),

    suppressWarnings(!is.na(as.numeric(height_chr))) ~
      as.numeric(height_chr),

    TRUE ~ NA_real_
  )
}

# Step 4: Create Combine Summary Tables ----
make_combine_table <- function(position_code) {
  Combine_All |>
    filter(pos == position_code) |>
    mutate(height_inches = clean_height_inches(ht)) |>
    group_by(season) |>
    summarise(
      player_count = n(),
      avg_height_inches = round(mean(height_inches, na.rm = TRUE), 1),
      avg_weight = round(mean(wt, na.rm = TRUE), 1),
      avg_forty = round(mean(forty, na.rm = TRUE), 2),
      avg_vertical = round(mean(vertical, na.rm = TRUE), 1),
      avg_bench = round(mean(bench, na.rm = TRUE), 1),
      avg_cone = round(mean(cone, na.rm = TRUE), 2),
      .groups = "drop"
    ) |>
    arrange(season)
}

WR_Combine_Table <- make_combine_table("WR")
RB_Combine_Table <- make_combine_table("RB")

# Step 5: Calculate WR Receiving Yards Per Game ----
WR_YPG_Avg <- Player_Stats_All |>
  filter(position == "WR", season_type == "REG") |>
  group_by(season, player_id, player_name) |>
  summarise(
    games_played = n_distinct(week),
    total_rec_yards = sum(receiving_yards, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(games_played >= 3) |>
  mutate(player_ypg = total_rec_yards / games_played) |>
  group_by(season) |>
  summarise(avg_wr_ypg = mean(player_ypg, na.rm = TRUE), .groups = "drop")

# Step 6: Calculate RB Rushing Yards Per Game ----
RB_YPG_Avg <- Player_Stats_All |>
  filter(position == "RB", season_type == "REG") |>
  group_by(season, player_id, player_name) |>
  summarise(
    games_played = n_distinct(week),
    total_rushing = sum(rushing_yards, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(games_played >= 3) |>
  mutate(player_ypg = total_rushing / games_played) |>
  group_by(season) |>
  summarise(avg_rb_ypg = mean(player_ypg, na.rm = TRUE), .groups = "drop")

# Step 7: Create Dual-Axis Plot Function ----
make_dual_axis_plot <- function(data, x_var, athletic_var, production_var,
                                athletic_label, production_label,
                                title_text, subtitle_text) {

  athletic_range <- range(data[[athletic_var]], na.rm = TRUE)
  production_range <- range(data[[production_var]], na.rm = TRUE)

  scale_factor <- diff(athletic_range) / diff(production_range)
  shift <- athletic_range[1] - production_range[1] * scale_factor

  plot_data <- data |>
    mutate(production_scaled = .data[[production_var]] * scale_factor + shift)

  ggplot(plot_data, aes(x = .data[[x_var]])) +
    geom_line(aes(y = .data[[athletic_var]], color = athletic_label),
              linewidth = 1.2) +
    geom_point(aes(y = .data[[athletic_var]], color = athletic_label),
               size = 3) +
    geom_line(aes(y = production_scaled, color = production_label),
              linewidth = 1.2, linetype = "dashed") +
    geom_point(aes(y = production_scaled, color = production_label),
               size = 3) +
    scale_y_continuous(
      name = athletic_label,
      sec.axis = sec_axis(
        transform = ~ (. - shift) / scale_factor,
        name = production_label
      )
    ) +
    scale_x_continuous(breaks = years) +
    labs(
      title = title_text,
      subtitle = subtitle_text,
      x = "Season / Combine Year",
      color = NULL
    ) +
    theme_minimal(base_size = 13) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5, color = "grey40"),
      legend.position = "bottom"
    )
}

# Step 8: Build WR Plots ----
Combine_WR_Cone_Avg <- Combine_All |>
  filter(pos == "WR", !is.na(cone)) |>
  group_by(season) |>
  summarise(avg_cone = mean(cone, na.rm = TRUE), .groups = "drop")

TCD_WRYPG_Data <- inner_join(Combine_WR_Cone_Avg, WR_YPG_Avg, by = "season")

TCD_WRYPG_Plot <- make_dual_axis_plot(
  data = TCD_WRYPG_Data,
  x_var = "season",
  athletic_var = "avg_cone",
  production_var = "avg_wr_ypg",
  athletic_label = "Avg 3-Cone Drill Time (seconds) — lower is faster",
  production_label = "Avg WR Receiving Yards Per Game",
  title_text = "NFL Combine WR 3-Cone Drill vs. WR Receiving Yards Per Game",
  subtitle_text = "Combine classes 2016–2025 | Regular season stats 2016–2025"
)

Combine_WR_Forty_Avg <- Combine_All |>
  filter(pos == "WR", !is.na(forty)) |>
  group_by(season) |>
  summarise(avg_forty = mean(forty, na.rm = TRUE), .groups = "drop")

Forty_WRYPG_Data <- inner_join(Combine_WR_Forty_Avg, WR_YPG_Avg, by = "season")

Forty_WRYPG_Plot <- make_dual_axis_plot(
  data = Forty_WRYPG_Data,
  x_var = "season",
  athletic_var = "avg_forty",
  production_var = "avg_wr_ypg",
  athletic_label = "Avg 40-Yard Dash Time (seconds) — lower is faster",
  production_label = "Avg WR Receiving Yards Per Game",
  title_text = "NFL Combine WR 40-Yard Dash vs. WR Receiving Yards Per Game",
  subtitle_text = "Combine classes 2016–2025 | Regular season stats 2016–2025"
)

# Step 9: Build RB Plots ----
Combine_RB_Cone_Avg <- Combine_All |>
  filter(pos == "RB", !is.na(cone)) |>
  group_by(season) |>
  summarise(avg_cone = mean(cone, na.rm = TRUE), .groups = "drop")

TCD_RBYPG_Data <- inner_join(Combine_RB_Cone_Avg, RB_YPG_Avg, by = "season")

TCD_RBYPG_Plot <- make_dual_axis_plot(
  data = TCD_RBYPG_Data,
  x_var = "season",
  athletic_var = "avg_cone",
  production_var = "avg_rb_ypg",
  athletic_label = "Avg 3-Cone Drill Time (seconds) — lower is faster",
  production_label = "Avg RB Rushing Yards Per Game",
  title_text = "NFL Combine RB 3-Cone Drill vs. RB Rushing Yards Per Game",
  subtitle_text = "Combine classes 2016–2025 | Regular season stats 2016–2025"
)

Combine_RB_Forty_Avg <- Combine_All |>
  filter(pos == "RB", !is.na(forty)) |>
  group_by(season) |>
  summarise(avg_forty = mean(forty, na.rm = TRUE), .groups = "drop")

Forty_RBYPG_Data <- inner_join(Combine_RB_Forty_Avg, RB_YPG_Avg, by = "season")

Forty_RBYPG_Plot <- make_dual_axis_plot(
  data = Forty_RBYPG_Data,
  x_var = "season",
  athletic_var = "avg_forty",
  production_var = "avg_rb_ypg",
  athletic_label = "Avg 40-Yard Dash Time (seconds) — lower is faster",
  production_label = "Avg RB Rushing Yards Per Game",
  title_text = "NFL Combine RB 40-Yard Dash vs. RB Rushing Yards Per Game",
  subtitle_text = "Combine classes 2016–2025 | Regular season stats 2016–2025"
)

# Step 10: Display Tables and Plots ----
kable(WR_Combine_Table)
kable(RB_Combine_Table)

TCD_WRYPG_Plot
Forty_WRYPG_Plot
TCD_RBYPG_Plot
Forty_RBYPG_Plot
```
