---
title: "NFL Combine Running Back Analysis"
author: "Ronish Padhy, Dylan Mckean,  Abhijay Madanagopal"
format: pdf
---
## Introduction

This project analyzes NFL Combine measurements for running backs from 2016 to 2025. The goal is to examine athletic testing trends such as height, weight, 40-yard dash time, vertical jump, bench press reps, and 3-cone drill time. These combine measurements are then compared with running back rushing production to see whether any possible patterns appear between testing results and on-field performance.

Right now, this analysis focuses only on running backs. In the future, the same process could be expanded to other positions such as quarterbacks, wide receivers, or defensive backs.

## Load Packages

```{r}
library(tidyverse)
library(nflreadr)
library(ggplot2)
library(knitr)
library(dplyr)
library(stringr)
```

## Load Data

```{r}
Combine_2016 <- load_combine(2016)
Combine_2017 <- load_combine(2017)
Combine_2018 <- load_combine(2018)
Combine_2019 <- load_combine(2019)
Combine_2020 <- load_combine(2020)
Combine_2021 <- load_combine(2021)
Combine_2022 <- load_combine(2022)
Combine_2023 <- load_combine(2023)
Combine_2024 <- load_combine(2024)
Combine_2025 <- load_combine(2025)

Player_Stats_2016 <- load_player_stats(2016)
Player_Stats_2017 <- load_player_stats(2017)
Player_Stats_2018 <- load_player_stats(2018)
Player_Stats_2019 <- load_player_stats(2019)
Player_Stats_2020 <- load_player_stats(2020)
Player_Stats_2021 <- load_player_stats(2021)
Player_Stats_2022 <- load_player_stats(2022)
Player_Stats_2023 <- load_player_stats(2023)
Player_Stats_2024 <- load_player_stats(2024)
Player_Stats_2025 <- load_player_stats(2025)
```

## Running Back Combine Measurements

The table below summarizes average NFL Combine measurements for running backs from 2016 to 2025. It includes the number of running backs recorded each year, along with average height, weight, 40-yard dash time, vertical jump, bench press reps, and 3-cone drill time.

```{r}
Combine_All <- bind_rows(
  Combine_2016,
  Combine_2017,
  Combine_2018,
  Combine_2019,
  Combine_2020,
  Combine_2021,
  Combine_2022,
  Combine_2023,
  Combine_2024,
  Combine_2025
)

Combine_All_RB_Table <- Combine_All |>
  filter(pos == "RB") |>
  mutate(
    height_inches = case_when(
      str_detect(as.character(ht), "^\\d-\\d{1,2}$") ~
        as.numeric(str_extract(as.character(ht), "^\\d")) * 12 +
        as.numeric(str_extract(as.character(ht), "\\d{1,2}$")),
      suppressWarnings(!is.na(as.numeric(ht))) ~ as.numeric(ht),
      TRUE ~ NA_real_
    )
  ) |>
  group_by(season) |>
  summarise(
    rb_count = n(),
    avg_height_inches = round(mean(height_inches, na.rm = TRUE), 1),
    avg_weight = round(mean(wt, na.rm = TRUE), 1),
    avg_forty = round(mean(forty, na.rm = TRUE), 2),
    avg_vertical = round(mean(vertical, na.rm = TRUE), 1),
    avg_bench = round(mean(bench, na.rm = TRUE), 1),
    avg_cone = round(mean(cone, na.rm = TRUE), 2),
    .groups = "drop"
  ) |>
  arrange(season)

kable(
  Combine_All_RB_Table,
  caption = "Average NFL Combine Measurements for Running Backs by Season",
  col.names = c(
    "Season",
    "RB Count",
    "Avg Height (inches)",
    "Avg Weight",
    "Avg 40-Yard Dash",
    "Avg Vertical",
    "Avg Bench Reps",
    "Avg 3-Cone"
  )
)
```

Overall, running back measurements stay pretty consistent across the years. Average height is usually around 70 inches, and average weight mostly stays between 206 and 218 pounds. Speed and explosiveness move slightly more. The fastest average 40-yard dash appears in 2025, and 2025 also has the highest average vertical jump. Some values appear as missing because the dataset does not always include usable results for every drill in every season.

## Running Back Rushing Production

This section calculates average rushing yards per game for running backs during the regular season. Players with fewer than three games played are removed so that one-game outliers do not distort the averages.

```{r}
Player_Stats_All <- bind_rows(
  Player_Stats_2016,
  Player_Stats_2017,
  Player_Stats_2018,
  Player_Stats_2019,
  Player_Stats_2020,
  Player_Stats_2021,
  Player_Stats_2022,
  Player_Stats_2023,
  Player_Stats_2024,
  Player_Stats_2025
)

RB_YPG_Avg <- Player_Stats_All |>
  filter(season_type == "REG", position == "RB") |>
  group_by(season, player_id, player_name) |>
  summarise(
    games_played  = n_distinct(week),
    total_rushing = sum(rushing_yards, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(games_played >= 3) |>
  mutate(ypg = total_rushing / games_played) |>
  group_by(season) |>
  summarise(
    avg_rb_ypg = mean(ypg, na.rm = TRUE),
    .groups = "drop"
  )

kable(
  RB_YPG_Avg,
  caption = "Average Running Back Rushing Yards Per Game by Season",
  col.names = c("Season", "Average RB Rushing Yards Per Game")
)
```

## Three-Cone Drill and Rushing Production

The 3-cone drill measures agility and change of direction. Lower times are better. This graph compares average running back 3-cone drill time with average rushing yards per game.

```{r}
Combine_RB_Avg <- Combine_All |>
  filter(pos == "RB") |>
  filter(!is.na(cone)) |>
  group_by(season) |>
  summarise(
    avg_cone = mean(cone, na.rm = TRUE),
    .groups = "drop"
  )

TCD_RBYPG_Data <- inner_join(Combine_RB_Avg, RB_YPG_Avg, by = "season")

cone_range <- range(TCD_RBYPG_Data$avg_cone)
ypg_range <- range(TCD_RBYPG_Data$avg_rb_ypg)

scale_factor <- diff(cone_range) / diff(ypg_range)
shift <- cone_range[1] - ypg_range[1] * scale_factor

TCD_RBYPG_Data <- TCD_RBYPG_Data |>
  mutate(ypg_scaled = avg_rb_ypg * scale_factor + shift)

TCD_RBYPG_Plot <- ggplot(TCD_RBYPG_Data, aes(x = season)) +
  geom_line(aes(y = avg_cone, color = "Avg 3-Cone (sec)"),
            linewidth = 1.2) +
  geom_point(aes(y = avg_cone, color = "Avg 3-Cone (sec)"),
             size = 3) +
  geom_line(aes(y = ypg_scaled, color = "Avg RB Rush YPG"),
            linewidth = 1.2, linetype = "dashed") +
  geom_point(aes(y = ypg_scaled, color = "Avg RB Rush YPG"),
             size = 3) +
  scale_y_continuous(
    name = "Avg 3-Cone Drill Time (seconds)",
    sec.axis = sec_axis(
      transform = ~ (. - shift) / scale_factor,
      name = "Avg RB Rushing Yards Per Game"
    )
  ) +
  scale_x_continuous(breaks = 2016:2025) +
  scale_color_manual(
    values = c("Avg 3-Cone (sec)" = "#003f5c",
               "Avg RB Rush YPG" = "#ff6361")
  ) +
  labs(
    title = "NFL Combine RB 3-Cone Drill vs. RB Rushing Yards Per Game",
    subtitle = "Combine classes 2016–2025 | Regular season stats 2016–2025",
    x = "Season / Combine Year",
    color = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title    = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, color = "grey40"),
    legend.position = "bottom",
    axis.title.y.left  = element_text(color = "#003f5c"),
    axis.title.y.right = element_text(color = "#ff6361")
  )

TCD_RBYPG_Plot
```

The graph helps compare agility testing with rushing production. Since the two measurements use different scales, rushing yards per game is transformed onto the same visual space. This makes the two trends easier to compare, but it should not be treated as proof that 3-cone time directly causes better rushing production.

## Forty-Yard Dash and Rushing Production

The 40-yard dash measures straight-line speed. Lower times are better. This graph compares average running back 40-yard dash time with average rushing yards per game.

```{r}
Combine_RB_Forty_Avg <- Combine_All |>
  filter(pos == "RB") |>
  filter(!is.na(forty)) |>
  group_by(season) |>
  summarise(
    avg_forty = mean(forty, na.rm = TRUE),
    .groups = "drop"
  )

Forty_RBYPG_Data <- inner_join(Combine_RB_Forty_Avg, RB_YPG_Avg, by = "season")

forty_range <- range(Forty_RBYPG_Data$avg_forty)
ypg_range <- range(Forty_RBYPG_Data$avg_rb_ypg)

scale_factor <- diff(forty_range) / diff(ypg_range)
shift <- forty_range[1] - ypg_range[1] * scale_factor

Forty_RBYPG_Data <- Forty_RBYPG_Data |>
  mutate(ypg_scaled = avg_rb_ypg * scale_factor + shift)

Forty_RBYPG_Plot <- ggplot(Forty_RBYPG_Data, aes(x = season)) +
  geom_line(aes(y = avg_forty, color = "Avg 40-Yard Dash (sec)"),
            linewidth = 1.2) +
  geom_point(aes(y = avg_forty, color = "Avg 40-Yard Dash (sec)"),
             size = 3) +
  geom_line(aes(y = ypg_scaled, color = "Avg RB Rush YPG"),
            linewidth = 1.2, linetype = "dashed") +
  geom_point(aes(y = ypg_scaled, color = "Avg RB Rush YPG"),
             size = 3) +
  scale_y_continuous(
    name = "Avg 40-Yard Dash Time (seconds)",
    sec.axis = sec_axis(
      transform = ~ (. - shift) / scale_factor,
      name = "Avg RB Rushing Yards Per Game"
    )
  ) +
  scale_x_continuous(breaks = 2016:2025) +
  scale_color_manual(
    values = c("Avg 40-Yard Dash (sec)" = "#003f5c",
               "Avg RB Rush YPG" = "#ff6361")
  ) +
  labs(
    title = "NFL Combine RB 40-Yard Dash vs. RB Rushing Yards Per Game",
    subtitle = "Combine classes 2016–2025 | Regular season stats 2016–2025",
    x = "Season / Combine Year",
    color = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, color = "grey40"),
    legend.position = "bottom",
    axis.title.y.left = element_text(color = "#003f5c"),
    axis.title.y.right = element_text(color = "#ff6361")
  )

Forty_RBYPG_Plot
```

This graph compares speed with rushing production. Like the 3-cone graph, it is useful for spotting possible patterns, but it does not prove that faster 40-yard dash times automatically lead to better NFL rushing production.

## Conclusion and Next Steps

This analysis shows that running back combine measurements from 2016 to 2025 are mostly stable. Average height and weight do not change much, while speed, explosiveness, and agility vary slightly by year. The combine table gives useful background, and the graphs help compare testing results with rushing yards per game.

At this stage, the project is focused only on running backs. The next step would be to expand the same type of analysis to other positions, especially quarterbacks. For quarterbacks, the analysis would need different performance statistics, such as passing yards, rushing yards, completion percentage, or total offensive production. This would make the project stronger because it would compare how different combine measurements matter for different positions.